Geometrization of characters of smooth group schemes over finite fields\\ with an application to types for supercuspidal representations

### 2016-03-03 followup.tex
Adding reference to Gurevich-Hadani preprint

It is one of the main results of \cite{gurevich-hadani:07a} that there is a Weil sheaf complex $\cs{W}_{\psi}$ on $\Sp(V)\ltimes V^\sharp$ such that 
\begin{equation}
\trFrob{\cs{W}_\psi} = \trace(W_\psi).
\end{equation}
%
Although nothing more that this statement will be needed below, the construction of $\cs{W}_\psi$ is so unbelievably gorgeous that we can't resist saying a few extra words about it here.
The reader pressed for time is invited to skip to the next section without loosing anything needed for the arguments in the rest of Section~\ref{sec:types}.

>>>>

It is one of the main results of \cite{gurevich-hadani:07a} (see also \cite{gurevich-hadani:11a}*{Thm. 4.5}) that there is a Weil sheaf complex $\cs{W}_{\psi}$ on $\Sp(V)\ltimes V^\sharp$ such that 
\begin{equation}
\trFrob{\cs{W}_\psi} = \trace(W_\psi).
\end{equation}
%
Although nothing more that this statement will be needed below, the construction of $\cs{W}_\psi$ is so unbelievably gorgeous that we can't resist saying a few extra words about it here.
The reader pressed for time is invited to skip to the next section without loosing anything needed for the arguments in the rest of Section~\ref{sec:types}.
